Hardware-accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-04-22 paper.tex
Clarified last sentence of paragraph about application
Fixed order of 'they' in questions in evaluation section
Note some libraries require Poco, GLFW, and/or CppUnit

All of the libraries can be compiled as shared libraries using GCC on Linux and
Mac OS X.

From there an application was created to view RapidGL scenes.  Users can
rotate the camera around a scene, as well as select objects and drag them.  It
shows the current frame rate so we can evaluate the performance of the scenes.

@@

How fast they can be rendered?
How easy they were to implement?

>>>>

All of the libraries can be compiled as shared libraries using GCC on Linux and
Mac OS X.  Some libraries require {\em Poco} for text and XML utilities.  {\em
GLFW} and {\em CppUnit} are also required by some libraries for unit testing.

From there an application was created to view RapidGL scenes.  Users can
rotate the camera around a scene, as well as select objects and drag them.  The
application shows the current frame rate so the performance of a scene can be
evaluated.

@@

How fast can they be rendered?
How easy were they to implement?
